---
title: "lab-07-simpsons.Rmd"
author: " Walaa Ali "
date: "3 March 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r load_libraries, message=FALSE}
library(tidyverse) 
library(mosaicData)
```


## Exercises


1.  
```{r whickam}
?Whickham
```
    
Your answer:
The data is observational as the description states that is based on age, smoking, and mortality, which are all observable events and not produced via experiments.



2.  
```{r observations}
nrow(Whickham)

```

Your answer;
obs 1314  var 3
Each row represents age, whether or not it is a smoker, and is it alive or not

3.  

```{r number_variables}
names(Whickham)
```

Your answer:  there are 3 variables, "0utcome","smoker", and "age"
outcome (factor)
age(integer)
smoker(factor)
```{r var_type}
class(Whickham$outcome)
class(Whickham$age)
class(Whickham$smoker)
```

Your answer: I expect that health will deteriorate with the passage of time, too, the incidence of cancer, and if he continues to smoke, he may lead to death.

```{r plot_outcome}
ggplot(Whickham, aes(x = smoker))
geom_bar()
```


```{r plot_smoker}
ggplot(Whickham, aes(x = smoker)) +
  geom_bar()
```

```{r plot_age}
ggplot(Whickham, aes(x = age)) +
  geom_boxplot()
```


4. 

```{r plot_smokeVSincome_1}
ggplot(data=Whickham, aes(x=smoker, y=outcome, color=outcome)) + geom_bar(stat="identity")
```

Knit, commit, and push to github.

5. 

```{r plot_smokeVSincome_2}
Whickham %>%
  count(smoker, outcome)
```

6.

```{r age_cat}

```

7. 

```{r plot_smokeVSincome_3}

```

Knit, commit, and push to github.